### 2016-10-09 text/MS.Rmd
reshaped code to work with remake

```{r, results="hide", warnings=FALSE, echo=FALSE, message=FALSE}
load('../output/RDatafiles/analyses.RData')
load('../output/RDatafiles/numbers.RData')
source('../R/functions-analyses.R')
source('../R/functions-figures.R')
cleanbib()
myRefs   <-  listBibs()
exporBibs(myRefs, erase=TRUE)
```
**Temperature effects on mass-scaling exponents in colonial animals: a manipulative test**

@@

*3. Respiration measurements*  
Individual metabolic rates (converted to $\mu$l $\textrm{O}_\textrm{2}$ h^-1^, *n* = `r nrow(metRates)`), $B_i$, were measured as rate of oxygen consumption, $\dot{V}\textrm{O}_\textrm{2}$, of colony fragments at nominal temperatures of 10 or 25 ˚C. All individuals (regardless of size) and species were randomly assigned to test temperatures, and we used replicate vials and controlled temperature cabinets (see below). Measurements were conducted using a 144-channel PreSens Sensor Dish Reader (SDR, AS-1 Scientific, Wellington, New Zealand) according to standard techniques `r myCite(c('koster2008meps', 'lighton2008book', 'white2011amnat'))`.  $\dot{V}\textrm{O}_\textrm{2}$ was measured by placing the colony fragment in a glass vial containing 0.2$\mu$m filtered sea water and a non-consumptive $\textrm{O}_\textrm{2}$ sensor spot and calculated from the rate of change of $\textrm{O}_\textrm{2}$ saturation ($m_a$, \% h^‑1^) as:

@@

>>>>

**Temperature effects on mass-scaling exponents in colonial animals: a manipulative test**

@@

*3. Respiration measurements*  
Individual metabolic rates (converted to $\mu$l $\textrm{O}_\textrm{2}$ h^-1^, *n* = `r nrow(numbersList$metRates)`), $B_i$, were measured as rate of oxygen consumption, $\dot{V}\textrm{O}_\textrm{2}$, of colony fragments at nominal temperatures of 10 or 25 ˚C. All individuals (regardless of size) and species were randomly assigned to test temperatures, and we used replicate vials and controlled temperature cabinets (see below). Measurements were conducted using a 144-channel PreSens Sensor Dish Reader (SDR, AS-1 Scientific, Wellington, New Zealand) according to standard techniques `r myCite(c('koster2008meps', 'lighton2008book', 'white2011amnat'))`.  $\dot{V}\textrm{O}_\textrm{2}$ was measured by placing the colony fragment in a glass vial containing 0.2$\mu$m filtered sea water and a non-consumptive $\textrm{O}_\textrm{2}$ sensor spot and calculated from the rate of change of $\textrm{O}_\textrm{2}$ saturation ($m_a$, \% h^‑1^) as:

@@

```{r, echo=FALSE}
ci95Estimates     <-  numbersList$ci95Estimates
metabolicDiff     <-  numbersList$metabolicDiff
averageEstimates  <-  numbersList$averageEstimates
q10andErs         <-  numbersList$q10andErs
tempDeltas        <-  numbersList$tempDeltas
```
